
---
title: "Guest Summary and Invoice – Jon & Cyrena’s Wedding"
output: pdf_document
params:
  party_name: NULL
  guests: NULL
  arrival_days: NULL
  total_due: NULL
  guests_df: NULL
  staying_sunday: NULL
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(dplyr)
```
**Dear `r paste(params$guests, collapse = " & ")`,**
We are thrilled to welcome you to Isabella Freedman Jewish Retreat Center for Jon & Cyrena's wedding weekend, June 20–22, 2025. Below, you’ll find important details about your stay, followed by your transaction summary.
\vspace{1em}
\hrule
### Arrival & Departure
`r if ("Friday" %in% params$arrival_days) {"Friday arrivals begin at 3 PM on Friday, June 20.\n"}`  
`r if ("Saturday" %in% params$arrival_days) {"Saturday arrivals may check in anytime, starting with 8 AM breakfast.\n"}`  
Check-in is located in the Main Building, the large red building at the center of campus.

Guests departing Sunday, June 22, may check out anytime after the reception.  
Guests staying Sunday night must check out by 11 AM on Monday, June 23.
\vspace{1em}
\hrule
### Driving & Parking
**Address:** 116 Johnson Rd, Falls Village, CT 06031  
**Parking Areas:**  
- Main Lot: Next to the office by the main entrance  
- Barnyard Lot: At the other end of campus  
- Accessible Parking: Across from the Main Building  
*Please do not park on the grass or in front of guest buildings.*
\vspace{1em}
\hrule
### Train Transportation
From NYC: 30 mins from Wassaic Station (Metro-North Harlem Line)  
**Taxis (no Uber/Lyft):**  
Watson Livery: 845-464-8178  
Morning Star Taxi: 845-200-9430  
Jon & Cyrena will share a carpool sign-up and shuttle info soon.
\vspace{1em}
\hrule
### Outside Food Policy
One of our mashgichim (kosher supervisors) must pre-approve all food items that enter the designated dining spaces. If you plan to supplement our delicious, healthy, farm-to-table meals, your items must be completely sealed in original packaging. Unapproved food and drinks may be enjoyed anywhere on campus besides our dining spaces.

Your meals and provided and snacks available at all times, but feel free to bring additional snacks or drinks of your preference.
\vspace{1em}
\hrule
### Packing List
You may want to bring: medications, toiletries, a flashlight, chargers, a water bottle or mug, hiking shoes, a swimsuit, hat, sunglasses, sunblock, a jacket for cool mornings, and a raincoat.

We provide: linens & towels in rooms, A/C + heat, yoga mats, and blankets.
Snacks are available at all times through the weekend (including between meals)
\vspace{1em}
\hrule
### Transaction Summary

#### `r params$party_name` - Jon & Cyrena’s Wedding Weekend

```{r transaction_table, results='asis'}
cols_to_show <- c("name")
if (any(params$guests_df$`Friday Meal Cost` > 0)) cols_to_show <- c(cols_to_show, "Friday Meal Cost")
if (any(params$guests_df$`Friday Accommodation Cost` > 0)) cols_to_show <- c(cols_to_show, "Friday Accommodation Cost")
if (any(params$guests_df$`Saturday Meal Cost` > 0)) cols_to_show <- c(cols_to_show, "Saturday Meal Cost")
if (any(params$guests_df$`Saturday Accommodation Cost` > 0)) cols_to_show <- c(cols_to_show, "Saturday Accommodation Cost")
if (any(params$guests_df$`Sunday Meal Cost` > 0)) cols_to_show <- c(cols_to_show, "Sunday Meal Cost")
if (any(params$guests_df$`Sunday Accommodation Cost` > 0)) cols_to_show <- c(cols_to_show, "Sunday Accommodation Cost")

knitr::kable(params$guests_df[, cols_to_show], format = "pipe", digits = 2,
             col.names = c("Name", tail(cols_to_show, length(cols_to_show)-1)))
```

```{r sunday_note, results='asis'}
# Check if any guests in this party are staying Sunday night
if (params$staying_sunday) {
  cat("**Note:** Your Sunday stay is reserved at no additional charge.")
}
```

**Total Due:** `$` `r formatC(params$total_due, format = "f", digits = 2)`
\vspace{1em}
\hrule
### Questions
For the weekend schedule and FAQs, visit the wedding website [withjoy.com/cyrena-and-jon](https://withjoy.com/cyrena-and-jon)  
Password: `jonandcyrena`

For registration and payment questions, please contact:

**Simone Stallman** at Isabella Freedman — [simone.stallman@adamah.org](mailto:simone.stallman@adamah.org) | [(860) 824-5991](tel:+18608245991)

For all other wedding questions, please reach out to:  
**Jon** — [jongewirtzman@gmail.com](mailto:jongewirtzman@gmail.com) | [215-817-9072](tel:+12158179072)  
**Cyrena** — [cyrenakt@gmail.com](mailto:cyrenakt@gmail.com) | [774-271-1144](tel:+17742711144)
\vspace{1em}
\hrule

\begin{center}
\textbf{Adamah}\\
25 Broadway, Suite 1700, New York, NY 10004 \\
\href{tel:2126442332}{212.644.2332} \quad | \quad \href{mailto:info@hazon.org}{info@hazon.org}
\vspace{1em}
\textbf{Isabella Freedman Jewish Retreat Center}\\
116 Johnson Road, Falls Village, CT 06031 \\
\href{tel:2126442332}{(212) 644-2332 ext. 305} \quad | \quad \href{mailto:registrar@hazon.org}{registrar@hazon.org}
\end{center}
\begin{center}
\includegraphics[width=0.5\linewidth]{logo.pdf}
\end{center}